---
title: "Using `cookiemonster`"
output:
  word_document:
    reference_docx: /home/johannes/Downloads/Rethinking Documentation Creating Inclusive Computational Tools for Social Sciences.docx
---

## Reading and storing cookies

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(cookiemonster)
```

Instead, you can export the neccessary cookies from your browser, after visiting and/or logging in a website, using a browser extension.
I can recommend [“Get cookies.txt”](https://chrome.google.com/webstore/detail/get-cookiestxt-locally/cclelndahbckbenkjhflpdbgdldlbecc) for Chromium based browsers or [“cookies.txt”](https://addons.mozilla.org/en-US/firefox/addon/cookies-txt/) for Firefox.

copy example from package

```{r results='hide'}
file.copy(
  from = system.file("extdata", "cookies.txt", package = "cookiemonster"),
  to = "."
)
```

add to cookie jar

```{r}
add_cookies(cookiefile = "cookies.txt")
```

```{r echo=FALSE}
file.remove("cookies.txt")
```

## using `cookiemonster` with other packages
## Default cookie storage

default location

```{r}
default_jar()
```

change default

```{r}
options(cookie_dir = tempdir())
default_jar()
```

revert to original

```{r}
options(cookie_dir = NULL)
default_jar()
```

retrieve cookies

```{r}
get_cookies("https://hb.cran.dev")
```

## Using stored cookies with `httr2`

```{r}
library(httr2)
resp <- request("https://hb.cran.dev/cookies/set") |>
  req_options(cookie = get_cookies("https://hb.cran.dev", as = "string")) |>
  req_perform()

resp |> 
  resp_body_json()
```

## Using stored cookies with `httr`

```{r}
library(httr)
GET("https://hb.cran.dev/cookies/set", set_cookies(get_cookies("https://hb.cran.dev", as = "vector")))
```

## Using stored cookies with `curl`

```{r}
library(curl)
h <- new_handle()
handle_setopt(h, cookie = get_cookies("https://hb.cran.dev", as = "string"))
resp <- curl_fetch_memory("https://hb.cran.dev/cookies/set", handle = h)
jsonlite::fromJSON(rawToChar(resp$content))
```

if curl response contains new cookies

```{r}
h2 <- new_handle()
resp <- curl_fetch_memory("https://hb.cran.dev/cookies/set?new_cookies=moo", handle = h2)
handle_cookies(h2)
```

store them

```{r}
new_cookies <- handle_cookies(h2)
store_cookies(new_cookies)
get_cookies("https://hb.cran.dev")
```

Note that adding cookies for a domain will replace all previously stored cookies for this domain by default.

